---
title: "Simple document"
output: github_document

    
---
```{r,echo=FALSE, message=FALSE}
library(tidyverse)
```

DS_problem1 part1

```{r}
data("penguins", package = "palmerpenguins")
summary(penguins)
```
1.the data including species island bill_length_mm bill_depth_mm flipper_length_mm body_mass_g sex year 
2. the size is 344rows(with one row of NA) 8columns
we can use `r nrow(penguins)` and `r ncol(penguins)` to check out the 
3.the flipper length is `r mean(penguins$flipper_length_mm, na.rm=TRUE)` mm

part2
```{r}
penguins <- na.omit(penguins)
plot_df=
  tibble(
    bill_length_mm = penguins$bill_length_mm,
    flipper_length_mm = penguins$flipper_length_mm
  )
ggplot(plot_df,aes(x=bill_length_mm,y=flipper_length_mm))+geom_point(aes(color=penguins$species))
ggsave("scatterplot of h1.pdf")
```

H1_problem2
```{r}
df=tibble(
    norm_number = rnorm(10),
    norm_logic=norm_number>0,
    norm_charactor= as.character(norm_number),
    
    ##factor1= as.factor(norm),
    factor2=c(1,2,3,1,2,3,1,2,3,1),
    factor4=as.factor(factor2),
    norm_factor=factor(c("1","2","3","1","2","3","1","2","3","1"),levels=c("1","2","3"))
  )
```
The mean of norm_number is `r mean(pull(df,norm_number))`
The mean of norm_logic is `r mean(pull(df,norm_logic))`
The mean of norm_charactor is `r mean(pull(df,norm_charactor))`
The mean of norm_factor is `r mean(pull(df,norm_factor))`

```{r}
as.numeric(df$norm_charactor)
as.numeric(df$norm_factor)
```


The mean of charactor is `r mean(as.numeric(df$norm_charactor))`.
The mean of norm_factor is `r mean(as.numeric(df$norm_factor))`.

Note:pay attention to the type of each vector variable.